Object-Oriented Internet - Azure Interoperability

### 2020-12-05 Latex/Manuscript.tex
Final review of the latex text #37
- prepared 1.4.3-Shared after PS review
Final review of the latex text #37
- Up to Sect. 2 MP reviewed - working copy

      Optimization of the industrial processes requires further research on the integration of machine-centric systems with human-centric cloud-based services in the context of new emerging disciplines, namely Industry 4.0 and Industrial Internet of Things. This research aims at working out a new generic architecture and deployment scenario applicable to this integration. The reactive interoperability relationship of the interconnected nodes is proposed to deal with the network traffic propagation asymmetry or assets' mobility. Described solution based on the OPC Unified Architecture international standard relaxes issues related to the real-time multi-vendor environment. The discussion addressing the generic architecture concludes that the embedded gateway archetype best suits all requirements. To promote separation of concerns and reusability, the proposed architecture of the embedded gateway archetype has been implemented as a composable part of an existing OPC UA PubSub framework.

@@

\listoftodos[TODO list]

@@

A typical \textbf{human-centric} approach is a web-service supporting, for example, a web user interface (UI) to monitor conditions, and manage millions of devices and their data in a typical cloud-based IoT approach. It is characteristic that, in this case, any uncertainty and necessity to make a decision can be relaxed by human interaction. Coordination of robots behavior in a work-cell (automation islands) is a \textbf{machine-centric} example. In this case, it is essential that any human interaction is impractical or even impossible. This interconnection scenario requires the machine to machine communication (M2M) demanding multi-vendor devices integration.

From the M2M communication concept, a broader concept of a smart factory can be derived. In this concept, the mentioned robots are only executive assets of an integrated supervisory control system responsible for macro optimization of an industrial process composed into one whole. Deployment of the smart factory concept requires a hybrid solution and interconnection of the mentioned above heterogeneous environments. This approach is called the fourth industrial revolution and coined as Industry 4.0. It is worth stressing that machines - or more general assets - interconnection is not enough, and additionally, assets interoperability has to be expected for the deployment of this concept. In this case, multi-vendor integration makes communication standardization especially important, namely it is required that the payload of the message is standardized to be factored on the data  gathering site and consumed on the ultimate destination site.

@@

\begin{itemize}
      \item it is a globally shareable environment and can be also used by malicious users
      \item it offers only non-deterministic communication making integration of islands of automation designed against the real-time requirements a difficult task
\end{itemize}

@@

After dynamically attaching a new island of automation the control application (responsible for the data pulling) must be reconfigured for this interoperability scenario. In other words, in this case, the interactive communication relationship cannot be directly applied because the control application must be informed on how to pull data from a new source. As a result, a plug and produce scenario cannot be seamlessly applied. A similar drawback must be overcome if for security reasons suitable protection methods have been applied to make network traffic propagation asymmetric. It is accomplished using intermediary devices, for example, firewalls, to enforce traffic selective availability based on predetermined security rules against unauthorized access.

@@

Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} Cyber-Physical System (CPS) and \textbf{human-centric} cloud-based front-end can be implemented applying the following scenarios: \textbf{direct interconnection} or \textbf{gateway based interconnection} (Sect. \ref*{subs.architecture}).

By design, the direct approach requires that the cloud has to be compliant with the interoperability standard the CPS is built upon - it becomes a consistent part of the CPS. Data models, roles, and responsibility differences of both solutions make this approach impractical or even imposable to be applied in typical cases. A more detailed description is covered by the Sect.~\ref*{cloud-to-sensors-field-level-connectivity}.

This article addresses further research on the integration of the CPS in the context of new emerging disciplines, i.e.~Industry 4.0 (I4.0) and the Industrial Internet of Things (IIoT). The new architecture is proposed for integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end. To support the multi-vendor environment OPC Unified Architecture \cite{LiteratureSurveyOnOpenPlatformCommunications} interoperability standard has been selected. The proposals are backed by proof of concept reference implementations. Prototyping addresses Microsoft Azure Cloud as an example. The prototyping outcome has been just published on GitHub as the open-source (MIT licensed) \todo{Add reference}. The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet.

@@

Using the session-oriented communication pattern it is difficult or even impossible to gather and process mobile data (Sec.~\ref*{introduction} ), which is one of the Internet of Things paradigms. OPC UA Part 14 PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} \todo{add ref: Mariusz Postol, UA Part 14: PubSub Main Technology Features in Object Oriented Internet, https://github.com/mpostol/OPC-UA-OOI, 2019, DOI: 10.5281/zenodo.1198852} offers the sessionless approach as an additional option to session based client-server interoperability relationship and is a consistent part of the OPC UA specifications suit. As the result it can be recognized as the IoT ready technology.

The presented proposals in the article are backed by proof of concept reference implementations. For this study, prototyping addresses Microsoft Azure cloud products. There are many reasons for selecting Azure to accomplish the cloud-based front-end of Cyber-Physical System (CPS). Azure offers Infrastructure as a Service (IaaS) and Platform as a Service (PaaS) capabilities. As a result, the platform can be used not only as a cloud-based front-end for CPS. By design, the Azure services are compliant with Security Development Lifecycle (SDL) an industry-leading security process. It is also compliant with the new international standard for cloud privacy, namely ISO 27018. Solutions hosted on Azure are scaled up to millions of users without any additional coding. For the development of the CPS front-end, it is essential that Azure provides very efficient storage services usefully for the purpose of real-time process data archival. Azure provides a vast variety of hybrid connections including but not limited to virtual private networks (VPNs), caches, content delivery networks (CDNs), ExpressRoute, and IoT dedicated services that can be directly used to implement cloud-based front-end for CPS. Because it is also integrated with other Microsoft tools like Office 365, Outlook, and SharePoint using Azure allows preserving investment and exporting process data to the mentioned tools. Azure also offers services supporting analytics and intelligence capabilities for further improving business processes and decision making. It is the only cloud platform that offers Blockchain as a Service (BaaS), Machine Learning, Bots, and Cognitive APIs capabilities.

Azure aids Internet protocols and open standards such as JSON, XML, SOAP, REST, MQTT, AMQP, and HTTP. A software development kits for C\#, Java, PHP, and Ruby are available for custom applications. Azure provides services supporting data exchange over the OPC UA, but they don't support PubSub compliant with the OPC UA Part-14\cite{RefWorks:doc:5d98837de4b055984c0eecf0}. Connectivity services on the network use JSON-based Data Transfer Object encoded based on schema derived from the solution metadata.

@@

Based on the sessionless and session-oriented communication patterns examination against the IoT requirements \cite{mpostol2020} it could be concluded that the connectionless pattern better suites issues related to the assets mobility and traffic asymmetry that is characteristic for the application domains in concern. Additionally, to promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} specification. According to proposed generic architecture (Fig.~\ref*{figure1.StrategyDomainModel}) to implement the \textit{Embedded\ Gateway} as a composable part of the \textit{Cyber-physical\ Node} a library implementing \textit{Networking} functionality in compliance with mentioned above specification is a starting point for further development. Additionally, it must be assumed that the library used to deploy \textit{Embedded\ Gateway} support dependency injection and be capable to compose an external part supporting Azure/PubSub gateway functionality. The composition process must be available without modification of the core code of an existing library. As a result, the prototyping is to be limited to implementation of the \textit{Embedded\ Gateway} software part only.

A library that meets all these requirements has been implemented consistently with the Object-Oriented Internet paradigm \cite{RefWorks:doc:5c66740ae4b081adf5804596} worked out in an open-source project \footnote{ \url{https://github.com/mpostol/OPC-UA-OOI} }. The paper \cite{mpostol2020} covers the description of a reference application program implementation proving that it is possible to design universal architecture targeting reactive interoperability as a consistent part of the Object-Oriented Internet concept compliant with the OPC UA PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} international standard. According to the presented implementation and evaluation, using the dependency injection and late binding, the application program can be seamlessly adapted to the production environment and scales well. This approach also improves flexibility and adaptability of the existing solutions against any modification of the production environment including but not limited to the selected interoperability standard change.

>>>>

      Optimization of the industrial processes requires further research on the integration of machine-centric systems with human-centric cloud-based services in the context of new emerging disciplines, namely Industry 4.0 and Industrial Internet of Things. This research aims at working out a new generic architecture and deployment scenario applicable to this integration. The reactive interoperability relationship of the interconnected nodes is proposed to deal with the network traffic propagation asymmetry or assets' mobility. Described solution based on the OPC Unified Architecture international standard relaxes issues related to the real-time multi-vendor environment. The discussion addressing the generic architecture concludes that the embedded gateway archetype best suits all requirements. To promote separation of concerns and reusability, the proposed architecture of the embedded gateway archetype has been implemented as a composable part of a selected OPC UA PubSub framework.

@@

%\listoftodos[TODO list]

@@

A typical \textbf{human-centric} approach is a web-service supporting, for example, a web user interface (UI) to monitor conditions and manage millions of devices and their data in a typical cloud-based IoT approach. In this case, it is characteristic that any uncertainty and necessity to make a decision can be relaxed by human interaction. Coordination of robots behavior in a work-cell (automation islands) is a \textbf{machine-centric} example. In this case, any human interaction must be recognized as impractical or even impossible. This interconnection scenario requires the machine to machine communication (M2M) demanding multi-vendor devices integration.

From the M2M communication concept, a broader idea of a smart factory can be derived. In this concept, the mentioned robots are only executive assets of an integrated supervisory control system responsible for macro optimization of an industrial process composed into one whole. Deployment of the smart factory concept requires a hybrid solution and interconnection of the mentioned above heterogeneous environments. This approach is called the fourth industrial revolution and was coined as Industry 4.0. It is worth stressing that machines - or more general assets - interconnection is not enough, and additionally, assets interoperability has to be expected for the deployment of this concept. In this case, multi-vendor integration makes communication standardization especially important, namely, it is required that the payload of the message is standardized to be factored on the data-gathering site and consumed on the ultimate destination site.

@@

\begin{itemize}
      \item it is a globally shareable and can be also used by malicious users
      \item it offers only non-deterministic communication making integration of islands of automation designed against the real-time requirements a difficult task
\end{itemize}

@@

After dynamically attaching a new island of automation the control application (responsible for the data pulling) must be reconfigured for this interoperability scenario. In other words, in this case, the interactive communication relationship cannot be directly applied because the control application must be informed on how to pull data from a new source. As a result, a plug and produce scenario \cite{PlugProduceByModellingSkills} cannot be seamlessly applied. A similar drawback must be overcome if for security reasons suitable protection methods have been applied to make network traffic propagation asymmetric. It is accomplished using intermediary devices, for example, firewalls, to enforce traffic selective availability based on predetermined security rules against unauthorized access.

@@

Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} Cyber-Physical System (CPS) and \textbf{human-centric} cloud-based front-end can be implemented applying the following scenarios: \textbf{direct} or \textbf{gateway} based interconnection (Sect. \ref*{subs.architecture}).

By design, the \textbf{direct} approach requires that the cloud has to be compliant with the interoperability standard the CPS is built upon - it becomes a consistent part of the CPS. Data models, roles, and responsibility differences of both solutions make this approach impractical or even imposable to be applied in typical cases. A more detailed description is covered by the Sect.~\ref*{cloud-to-sensors-field-level-connectivity}.

This article addresses further research on the integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M communication and emerging cloud computing as a \textbf{human-centric} front-end in the context of new emerging disciplines, i.e.~Industry 4.0 (I4.0) and the Industrial Internet of Things (IIoT). For this integration, a new architecture is proposed to promote communication parties reactive relationship. To support the multi-vendor environment OPC Unified Architecture \cite{LiteratureSurveyOnOpenPlatformCommunications} interoperability standard has been selected. The proposals are backed by proof of concept reference implementations. Prototyping addresses Microsoft Azure Cloud as an example. The prototyping outcome has been just published on GitHub as the open-source (MIT licensed) \todo{Add reference}. The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet \cite{RefWorks:doc:5c66740ae4b081adf5804596}.

@@

Using the session-oriented communication pattern it is difficult or even impossible to gather and process mobile data (Sec.~\ref*{introduction} ), which is one of the Internet of Things paradigms. OPC UA Part 14 PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0, UAPart14PubSubMainTechnologyFeatures} offers the sessionless approach as an additional option to session based client-server interoperability relationship and is a consistent part of the OPC UA specifications suit. As the result it can be recognized as the IoT ready technology.

The presented proposals in the article are backed by proof of concept reference implementations. For this study, prototyping addresses Microsoft Azure cloud products. There are many reasons for selecting Azure to accomplish the cloud-based front-end of Cyber-Physical System (CPS). Azure offers Infrastructure as a Service (IaaS) and Platform as a Service (PaaS) capabilities. As a result, the platform can be used not only as a cloud-based front-end for CPS. By design, the Azure services are compliant with Security Development Lifecycle (SDL) an industry-leading security process. It is also compliant with the new international standard for cloud privacy, namely ISO 27018. Solutions hosted on Azure are scaled up to millions of users without any additional coding. For the development of the todo front-end, it is essential that Azure provides very efficient storage services usefully for the purpose of real-time process data archival. Azure provides a vast variety of hybrid connections including but not limited to virtual private networks (VPNs), caches, content delivery networks (CDNs), ExpressRoute, and IoT dedicated services that can be directly used to implement cloud-based front-end for CPS. Because it is also integrated with other Microsoft tools like Office 365, Outlook, and SharePoint using Azure allows preserving investment and exporting process data to the mentioned tools. Azure also offers services supporting analytics and intelligence capabilities for further improving business processes and decision making. It is the only cloud platform that offers Blockchain as a Service (BaaS), Machine Learning, Bots, and Cognitive APIs capabilities.

Azure aids Internet protocols and open standards such as JSON, XML, SOAP, REST, MQTT, AMQP, and HTTP. A software development kits for C\#, Java, PHP, and Ruby are available for custom applications. Azure provides services supporting data exchange over the OPC UA, but they don't support PubSub compliant with the OPC UA Part-14. Connectivity services on the network use JSON-based Data Transfer Object encoded based on schema derived from the solution metadata.

@@

Based on the sessionless and session-oriented communication patterns examination against the IoT requirements \cite{mpostol2020} it could be concluded that the connectionless pattern better suites issues related to the assets mobility and traffic asymmetry that is characteristic for the application domains in concern. Additionally, to promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub  specification. According to proposed generic architecture (Fig.~\ref*{figure1.StrategyDomainModel}) to implement the \textit{Embedded\ Gateway} as a composable part of the \textit{Cyber-physical\ Node} a library implementing \textit{Networking} functionality in compliance with mentioned above specification is a starting point for further development. Additionally, it must be assumed that the library used to deploy \textit{Embedded\ Gateway} support dependency injection and be capable to compose an external part supporting Azure/PubSub gateway functionality. The composition process must be available without modification of the core code of an existing library. As a result, the prototyping is to be limited to implementation of the \textit{Embedded\ Gateway} software part only.

A library that meets all these requirements has been implemented consistently with the Object-Oriented Internet paradigm \cite{RefWorks:doc:5c66740ae4b081adf5804596} worked out in an open-source project \footnote{ \url{https://github.com/mpostol/OPC-UA-OOI} }. The paper \cite{mpostol2020} covers the description of a reference application program implementation proving that it is possible to design universal architecture targeting reactive interoperability as a consistent part of the Object-Oriented Internet concept compliant with the OPC UA PubSub international standard. According to the presented implementation and evaluation, using the dependency injection and late binding, the application program can be seamlessly adapted to the production environment and scales well. This approach also improves flexibility and adaptability of the existing solutions against any modification of the production environment including but not limited to the selected interoperability standard change.
